correlation_part2

### 2022-05-29 graphs_newt_snakes/correlation_part2.Rmd
made some more figures for the poster. started to look at the lond file named tall data. Made a back up snakemake file

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggmap)
library(ggplot2)
library(sf)
library(mapview)
library(ggpubr)
theme_set(theme_pubr())
```

@@

ggplot(data = world) +
  geom_sf() +
  geom_sf(data = states, fill = NA)+
  geom_point(data = snewt, aes(x = lon, y = lat, fill = mean_res), size = 5, shape = 22, ) +
  geom_point(data = snewt, aes(x = lon, y = lat, fill = mean_toxin), size = 3, shape = 21, ) +
  scale_fill_viridis_c()+
  coord_sf(xlim = c(-130.4494, -111.6764), ylim = c(29.742, 54.9415), expand = FALSE)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggmap)
library(ggplot2)
library(sf)
library(mapview)
library(ggpubr)
#theme_set(theme_pubr())
```

@@

ggplot(data = world) +
  geom_sf() +
  geom_sf(data = states, fill = NA)+
  geom_point(data = snewt, aes(x = lon, y = lat, fill = mean_res), size = 6, shape = 22, ) +
  geom_point(data = snewt, aes(x = lon, y = lat, fill = mean_toxin), size = 4, shape = 21, ) +
  scale_fill_viridis_c()+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
  coord_sf(xlim = c(-127, -115), ylim = c(34, 50.5), expand = FALSE)

ggplot(data = world) +
  geom_sf() +
  geom_sf(data = states, fill = NA)+
  #geom_point(data = snewt, aes(x = lon, y = lat, fill = mean_res), size = 6, shape = 22, ) +
  geom_point(data = snewt, aes(x = lon, y = lat, fill = mean_toxin), size = 4, shape = 21, ) +
  scale_fill_viridis_c()+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
  coord_sf(xlim = c(-127, -115), ylim = c(34, 50.5), expand = FALSE)

ggplot(data = world) +
  geom_sf() +
  geom_sf(data = states, fill = NA)+
  geom_point(data = snewt, aes(x = lon, y = lat, fill = mean_res), size = 6, shape = 22, ) +
  #geom_point(data = snewt, aes(x = lon, y = lat, fill = mean_toxin), size = 4, shape = 21, ) +
  scale_fill_viridis_c()+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
  coord_sf(xlim = c(-127, -115), ylim = c(34, 50.5), expand = FALSE)
